Macro drop and droplet profile detection during PGMAW process by image processing library

### 2010-12-30 articles/MIG/doc_broullion/latex/paper-drop.tex

\begin{document}

@@

A better comprehension of welding objects behavior presents in a PGMAW process
 as macro drop and metal transfer drop (droplet) could help to improve numerical simulations
 and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
% An example to this are the problems linked to productivity. To some process,
 For example, the
 increase of productivity means often increase of weld speed,
 however some welding defects related to bad shape, as the hump formations, limit the maximum weld 
 speed \cite{CHAPUIS,Mendez} and therefore the productivity. 
 In a PGMAW process, the weld quality is strongly relates with the metal transfer  stability 
 (the droplet deposition). The control of metal transfer process %implies control of
 will improve weld quality \cite{WANG}. In both example cases a macro drop kinetic
  study and a droplet dynamic analysis during static PGMAW process could help to better
 understand some GMAW related phenomena as humping formation \cite{CHO}, droplet 
  fluctuations \cite{WANG} that guarantee the welding quality. 
 In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
  geometrical analysis of macro drop and droplets in order to extract 
  qualitative information of these welding objects. 
  There have been many studies on visual sensing techniques for observing weld pool 
  image \cite{BAE} and metal transfer process during welding \cite{LIN}. Optical sensors like high speed 
 cameras and lighting systems have been widely use in GMAW process to realize 
 image acquisition \cite{GUANGJUN},
   control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
   Image processing plays a critical role in 
   extracting useful information from visual scenes \cite{WANG}.
 Nevertheless the strong interference from the arc lightning required more than standard 
   image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. 
Previous work has shown that is possible to perform geometrical 
   analysis in weld pools or droplets \cite{WU2}.
   Parameters such as macro drop or droplets surface, volumes 
or height has been measure using different and 
   specifics processing images algorithms \cite{WANG}, \cite{WU2}, \cite{SEED},
 \cite{NORDBRUCH}. However, to date, effectively automatic images processing
    of metal transfer has not been developed, possibly due to the  difficulty involved 
for welding researchers \cite{WANG}.

@@

\begin{equation}
B = \bigcup_{i}R_{i} 
\forall i  R_{i} \neq \emptyset
\forall i, j avec i \neq j\ R_{i}\bigcap R_{j} = \emptyset
\label{equation-segmentation}
\end{equation}

@@

\section*{References}
\begin{thebibliography}{10}
\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
(Reading, MA: Addison-Wesley)
\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
\end{thebibliography}

>>>>

\begin{document}
\bibliographystyle{unsrt}

@@

A better comprehension of welding objects behavior presents in a PGMAW process
 as macro drop and metal transfer drop (droplet) could help to improve numerical simulations
 and enhance welding quality in manufacturing process \cite{LIN}, \cite{WU1}.
% An example to this are the problems linked to productivity. To some process,
 For example, the
 increase of productivity means often increase of weld speed,
 however some welding defects related to bad shape, as the hump formations, limit the maximum weld 
 speed \cite{CHAPUIS,Mendez} and therefore the productivity. 
 In a PGMAW process, the weld quality is strongly relates with the metal transfer  stability 
 (the droplet deposition). The control of metal transfer process %implies control of
 will improve weld quality \cite{WANG}. In both example cases a macro drop kinetic
  study and a droplet dynamic analysis during static PGMAW process could help to better
 understand some GMAW related phenomena as humping formation \cite{CHO}, droplet 
  fluctuations \cite{WANG} that guarantee the welding quality. 
 In both case, the kinetic and the dynamic analysis, required the monitoring \cite{} and the 
  geometrical analysis of macro drop and droplets in order to extract 
  qualitative information of these welding objects. 
  There have been many studies on visual sensing techniques for observing weld pool 
  image \cite{BAE} and metal transfer process during welding \cite{LIN}. Optical sensors like high speed 
 cameras and lighting systems have been widely use in GMAW process to realize 
 image acquisition \cite{ZHANG4},
   control process \cite{BAE}, parametric studies \cite{BALSAMO} and droplet dynamics analysis\cite{LIN}.
   Image processing plays a critical role in 
   extracting useful information from visual scenes \cite{WANG}.
 Nevertheless the strong interference from the arc lightning required more than standard 
   image treatment to analyses the raw images of the welding process \cite{NORDBRUCH}. 
Previous work has shown that is possible to perform geometrical 
   analysis in weld pools or droplets \cite{WU1}.
   Parameters such as macro drop or droplets surface, volumes 
or height has been measure using different and 
   specifics processing images algorithms \cite{WANG}, \cite{WU1}, \cite{SEED},
 \cite{NORDBRUCH}. However, to date, effectively automatic images processing
    of metal transfer has not been developed, possibly due to the  difficulty involved 
for welding researchers \cite{WANG}.

@@

\begin{eqnarray}
B = \bigcup_{i}R_{i}\ \forall i \in \{0, \mbox{numbers of regions in B}\} \\
\mbox{with} R_{i} \neq \emptyset \\
\mbox{and}  R_{i}\bigcap R_{j} = \emptyset  \forall i, j\ \mbox{with}\ i \neq j\ 
\label{equation-segmentation}
\end{eqnarray}

@@

\bibliography{paper_bain}

%\section*{References}
%\begin{thebibliography}{10}
%\bibitem{book1} Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
%(Reading, MA: Addison-Wesley)
%\bibitem{eps} Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
%\end{thebibliography}
